ZCB Pricing

### 2018-08-02 ZCB Pricing .Rmd
Added some convergence tests

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
      sim_path[j,i] =s im_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

```{r 12}
#Stability

@@

>>>>

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

```{r 12}
#Stability Tests

@@

```{r 13}
# Convergence Tests
# Varying time steps

time_vec <- seq(0,100,1)

closed <- NULL
CN_conv <- NULL
Impl_conv <- NULL
Expl_conv <- NULL

for (i in 1:length(time_vec)){
  closed[i] <- bond_price()
}

for (i in 1:length(time_vec)){
  CN_conv[i] <- CN(I = 1:time_vec[i])
}

for (i in 1:length(time_vec)){
  Impl_conv[i] <- implicit(I = 1:time_vec[i])
}

for (i in 1:length(time_vec)){
  Expl_conv[i] <- explicit(I = 1:time_vec[i])
}

plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
lines(x = time_vec, y = CN_conv, type = "l", lty = 2)
lines(x = time_vec, y = Impl_conv, type = "l", lty = 3, col = "blue")
lines(x = time_vec, y = Expl_conv, type = "l", lty = 4, col = "red")
legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)
